Acceleration of Global Optimization Algorithm by Detecting Local Extrema Based on Machine Learning

### 2021-09-25 2021/Entropy/entropy.tex
First revision

%Russian
This paper aims to further develop the efficient deterministic global optimization method known as \textit{the information-statistical global search algorithm} \cite{Strongin2000}. The book referenced here contains the results of theoretical studies of the method that are of direct importance for its practical implementation. In particular, it discusses in detail the issues of convergence, the choice of parameters, and the conditions for stopping the algorithm, etc.
Note that the global search algorithm was originally designed for solving unconstrained optimization problems. Later, it was generalized to solve problems with non-convex constraints\cite{Barkalov2002} and multicriteria optimization problems \cite{Gergel2020}.
At the same time, scholars proposed various parallel versions of these algorithms, which can be used on modern supercomputers.\cite{Barkalov2016,globalizerSystem,Strongin2018}.

>>>>

%Russian
This paper aims to further develop the efficient deterministic global optimization method known as \textit{the information-statistical global search algorithm} \cite{Strongin2000}. The book referenced here contains the results of theoretical studies of the method that are of direct importance for its practical implementation. In particular, it discusses in detail the issues of convergence, the choice of parameters, and the conditions for stopping the algorithm, etc.
Note that the global search algorithm was originally designed for solving unconstrained optimization problems. Later, it was generalized to solve problems with non-convex constraints\cite{Barkalov2002} and multicriteria optimization problems \cite{Gergel2020}.
At the same time, scholars proposed various parallel versions of these algorithms, which can be used on modern supercomputers \cite{Barkalov2016,globalizerSystem,Strongin2018}.
